\documentclass[letterpaper,11pt,notitlepage]{article}
\usepackage{mystyle}
\usepackage{enumitem}
\begin{document}
\input{./title.tex}
\vbar
\head{Experience}
    \company{Heroku (subsidiary of Salesforce.com)}{2014-present}
        \companydescurl{A leading Platform-as-a-Service provider}{heroku.com} \\
        \postitle{Associate Member of Technical Staff, 2014 - 2015} \\
        \postitle{Member of Technical Staff, 2015 - 2016} \\
        \postitle{Senior Member of Technical Staff, 2016 - Present} \\
        \begin{employment}
            \item Quickly familiarised myself with and became productive in
              dozens of diverse codebases in multiple new-to-me languages (Ruby,
              Coffescript, Go, Erlang)
            \item Coordinated development with multiple teams to push
              cross-cutting projects forward
            \item Lead development on tooling to aid standards compliance,
                  allowing for new business opportunities
            \item Participated in 24/7 oncall rotation for high-impact services with
                  very low response times
            \item Coordinated responses to complex outages across multiple people
              and teams
            \item Predicted problems with architectural decisions before they
              became real world outages
            \item Helped launch several major features, including Heroku
              SSL, Automated Certificate Management, and dyno quotas
            \item Interacted directly with customers via internal support
              tickets
        \end{employment}
    \company{Demonware}{2012-2013}
    \companydescurl
       {Activision studio providing online infrastructure for multiplayer video
         games}
       {demonware.net} \\
        \postitle{Software Engineer, Systems Engineering (Co-op)}
        \begin{employment}
            \item Helped design, author, deploy, and support internal IaaS
                  project that drastically reduced datacentre buildout effort
            \item Maintained and updated metrics capability and infrastructure
            \item Wrote Puppet modules to deploy applications to thousands of servers
            \item Credited in several AAA video games, including
              {\it Diablo III} and multiple {\it Call of Duty} installments
        \end{employment}
    \company{Bering Media}{2011}
    \companydescurl
    {A small Toronto startup delivering geotargeted online marketing}
    {beringmedia.com} \\
    \postitle{Developer (Co-op)}
        \begin{employment}
            \item Developed internal web applications using PHP and Zend
            Framework
            \item Combined independently developed clustered components,
            utilizing Riak, Zookeeper and RabbitMQ
        \end{employment}
\vbar{}
\head{Education}
    \company{University of Toronto}{2010 -- 2014}
    \postitle{Honours Bachelor of Science}
    \begin{employment}
        \item Computer Science Specialist
        \item Writing and Rhetoric Minor
    \end{employment}
\newpage
%\vbar
\head{Technologies}
   \companydesc{I pride myself on learning new technologies fast, and making
     tactical changes in unfamiliar code-bases. These are some examples of
     technologies I've worked with in the past}
\begin{description}[topsep=0mm,noitemsep]
  \item[Python] The primary language of development at Demonware. Still my go-to
    for small scripts.
  \item[Ruby] Extensively used at Heroku, mostly Sinatra but some Rails.
  \item[Linux] Long-term user of desktop Arch Linux, have run CentOS,
    Gentoo and Ubuntu servers.
  \item[PostgresQL] The Database of choice at Heroku. Comfortable with raw SQL.
  %\item[Java] Coursework, some Android development (on GitHub)
  \item[Javascript] At Heroku I used both both server-side (Hubot)
    and client-side (internal tools).
  \item[Shell Scripting] Numerous shell scripts written, some under duress during incidents
  %\item[Puppet] Wrote modules for deploying and configuring in-house packages at Demonware
  \item[Haskell] Coursework and personal projects. Nothing professional yet, but I
    can dream.
  \item[Erlang] The Heroku Router is written in Erlang, as are various supporting services.
  %\item[Elixir] Several critical Heroku microservices are written in Elixir.
  \item[Go] Heroku extensively uses Go microservices with Kafka, gRPC, and Postgres.
\end{description}
\vbar
\head{Projects}
    \company{PleaseCaption}{2016}
    \companydesc{A bot to remind you to add alt text to your images}
    \begin{employment}
      \item Written in Haskell using Conduit
      \item \url{https://twitter.com/pleasecaption}
      \item \url{https://github.com/stillinbeta/pleasecaption}
    \end{employment}
    \company{Github}{}
        \begin{employment}
           \item \url{https://github.com/stillinbeta}
        \end{employment}
\vbar

\head{Talks}
      \company{Pager Equity}{}
      \companydesc{A talk on how a pager rotation could unintentionally be marginalising part of your team}
      \begin{employment}
          \item Given at Devops Days Boston 2016
          \item Recording: \url{http://bit.ly/liz-preso1}
          \item Slides: \url{http://bit.ly/liz-slides1}
      \end{employment}
      \company{Master of None}{}
      \companydesc{How I deal with being a generalist: learning new things fast,
      and making sure I can remember after I forget.}
      \begin{employment}
          \item Given at NYC SRE Tech Talks
          \item Slides: \url{http://bit.ly/liz-slides2}
      \end{employment}
\vbar
\head{Writing}
     \company{How Tech Employees Can Use Corporate Donation Matching}{2016}
     \companydesc{A how-to guide for leveraging corporate resources for
       activism}
     \begin{employment}
       \item Paid piece for Model View Culture
       \item \url{http://bit.ly/liz-article1}
       \end{employment}

\vbar
\head{Work Style}
\begin{description}[topsep=0mm,noitemsep]
  \item[Distributed] Heroku is entirely remote, so I'm familiar with
    geographically distributed teams.
  \item[Collaborative] I prefer to work closely with other engineers rather than
    in isolation.
  \item[Maintenance] Greenfield development is less interesting to me than maintaining
    and growing existing codebases.
\end{description}
\end{document}
